Rising from the Ashes II: A Hidden Abundance Bimodality in Illustris TNG

### 2024-09-03 paper/ms.tex
Bit more detail on plots

The main result of our paper is given in Figure~\ref{fig:fig1}. Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns). The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations. The \MgFe{} values in the lower panels are given offsets in order to reduce overlap. The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities. The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity. The two sequences merge around solar metallicity.

@@

The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles. In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SoI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right. We use age instead of formation time in order to better facilitate comparisons to observations. There is a gap in the ages that occurs at an age of $10.75\,\Gyr$, which we mark with a vertical dashed line. Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after. In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.

>>>>

The main result of our paper is given in Figure~\ref{fig:fig1}. Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns). The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}. We have applied the standard \texttt{scipy} implementation of a gaussian kernel density estimator to a Cartesian grid of points. For each panel, we normalize so that the integral of the distribution is unity. Colors are plotted in a log scale ranging from $0.08$ to $15\,\dex^{-2}$. Contour lines are plotted at $0.1$, $1.5$, and $10\,\dex^{-2}$.

The colored vertical lines are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations. The lower panels show 1D histograms of \MgFe{} in bins centered on these values. The bins for the Milky Way/simulations are $0.2$/$0.05\,\dex$. The \MgFe{} values are given offsets in order to reduce overlap. The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities. The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity. The two sequences merge around solar metallicity.

@@

The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles. In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SoI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right. We use age instead of formation time in order to better facilitate comparisons to observations. These panels are true 2D histograms, with a logarithmic colormap normalized to the maximum of the plot. The values of \MgFe{} are offset to avoid overlap.

There is a gap in the ages that occurs at an age of $10.75\,\Gyr$, which we mark with a vertical dashed line. Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after. In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.
